\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-10 manuscript/main.tex
renamed:    analysis/working on district level.do -> archive/working on district level.do 	modified:   manuscript/main.aux 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

To gather other characteristics information, we first extracted the POI data from the AutoNavi map using the web-scrawling Python program.\footnote{AutoNavi, a leading mapping application in China with a huge user base of more than 700 million, stands out for its detailed and accurate POI data and precise public transportation information. These features underscore AutoNavi's formidable lead in the digital mapping sector, highlighting its ability to provide unparalleled navigation accuracy and comprehensive urban mobility solutions. Our extracted AutoNavi map contains more than 1 million POIs for each city in each year.} We then classified the extracted POIs into different categories, the specifics of which are discussed in detail in Table \ref{tab:statistical}. This categorization was crucial for understanding the urban infrastructure and amenities available in the vicinity of the analyzed properties. We prioritized POIs within a 500-meter radius-a distance typically covered within a ten-minute walk, consistent with urban planning standards for accessible urban design. This radius was specifically chosen to reflect the immediate urban environment that influences residential desirability and value, as the majority of these POIs provide recreational services. Furthermore, some geo-informational data was also integrated into our research data, which consists of the annual gdp obtained from \citep{zhao_forecasting_2017}, nighttime lights data, obtained from \citep{elvidge_annual_2021} and air pollution data from \citep{doi:10.1021/acs.est.1c05309}. By merging these data with our research panel, we finally get the data.

@@

In the Appendix Table \ref{tab:sylized_fact_hetero_hhi} we also report the results of the robustness check of the dynamic model. The results show that the dynamic model Table \ref{tab:sylized_fact_hetero_mature}

>>>>

To gather additional characteristic information, we first extracted Point of Interest (POI) data from the AutoNavi map using a web-scraping Python program.\footnote{AutoNavi, a leading mapping application in China with a user base exceeding 700 million, is renowned for its detailed and accurate POI data as well as precise public transportation information. These features underscore AutoNavi's leadership in the digital mapping sector, highlighting its ability to provide unparalleled navigation accuracy and comprehensive urban mobility solutions. Our extracted AutoNavi dataset includes over one million POIs per city annually.} The extracted POIs were then classified into various categories, as detailed in Table \ref{tab
}. This classification is crucial for understanding the urban infrastructure and amenities available in the vicinity of the analyzed properties.

We matched each type of POI to the neighborhood-level data within a 500-meter radius, a distance typically covered by walking and consistent with urban planning standards for accessible urban design. This radius was also specifically selected to reflect the immediate urban environment influencing residential desirability and property values, as the majority of these POIs provide recreational services. Additionally, we integrated geo-informational data into our research, including annual GDP data from \citet{zhao_forecasting_2017}, nighttime lights data from \citet{elvidge_annual_2021}, and air pollution data from \citet{doi:10.1021/acs.est.1c05309}. We generated the centroid of the neighborhood-level data's polygon and then extracted the value from the geo-informational data. By merging these data sources with our research panel, we constructed a comprehensive research sample.

@@

To check the robustness of the result, we calculate the HHI index for each segmented market which is defined as $HHI = \sum_{i=1}^N (s_i)^2$ where $s_i$ is the market share of firm $i$ expressed as a percentage. Then we estimate the model by separating the samples to those with high HHI and low HHI where HHI is greater than 2000 and less than 2000. The results are shown in Table \ref{tab:sylized_fact_hetero_hhi}. The result indicates that

Moreover, to check the heterogeneity issue, we also classifies the we also report the results of the robustness check of the dynamic model. The results show that the dynamic model Table \ref{tab:sylized_fact_hetero_mature}
